The Distributed Nature of Copycat..? (WIP)

### 2017-11-15 papers/paper.tex
Adds random notes and plans

>>>>

\break
...
\break

And ten minutes later, it was done.
The "meta" formula performs as well as the "best" formula on the "ijjkkk" problem, which I consider the most novel.
Interestingly, I noticed that the paramterized formulas aren't as good on this problem. What did I parameterize them for? Was it well justified?

At this point, I plan on using the git branch "feature-normal-science-framework" to implement a system that takes in a problem set and provides several answer distributions as output.
Then, I'll do a massive cross-formula answer distribution comparison with $\chi^2$ tests. This will give me an idea about which formula and which changes are best.
I'll also be able to compare all of these answer distributions to the frequencies obtained in temperature removal branches of the repository.
